A Type System for Safe and Scalable Parallelism using Logical Regions

### 2012-07-11 doc/popl2013/related.tex

Reasoning about disjoint heap data is the strong suit of separation logic \cite{Reynolds02}.  
Concurrent separation logic\cite{Brookes04} has been 
used both to parallelize sequential programs\cite{Raza09,Gotsman07} and to provide 
a mechanism for reasoning about independence\cite{Hayman06}.
While we have borrowed some separation logic notation, we ultimately chose to use a 
permissions system as our primary formalism because separation logic does not easily
support the interleaving of operations to non-disjoint regions of memory.

>>>>

Reasoning about disjoint heap data is the strong suit of separation logic \cite{Reynolds02}.  
Concurrent separation logic\cite{Brookes04} has been 
used both to parallelize sequential programs\cite{Raza09,Gotsman07} and to provide 
a mechanism for reasoning about independence\cite{Hayman06}.
While we have borrowed some separation logic notation, we ultimately chose to use a 
permissions system as our primary formalism because separation logic does not easily
support reasoning about the interleaving of operations to non-disjoint regions of memory.
